---
title: "Assignment 1: R Markdown practice"
author: "FirstName LastName"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    smart: true
    dev: svg
urlcolor: blue
---

<!-- Write your Markdown below this line -->

# How the Course Works

The weekly interactive tutorials must be completed by the start of each week. Then each weekly assignment will be due at the end of the week.

# Course Goals

By the end of the course, students will be able to:

-   Use [GitHub](https://github.com/) for creating a reproducible research document

    -   My GitHub Username is: *erichan0411*

-   Obtain, clean, transform and visualize a dataset using the R programming Language.

-   Interpret and predict dataset trends using statistical inference and models.

-   Critically examine and interpret statistical claims reported in mass media.

# Including Code

## Running R code in a code chunk

```{r}
x <- 2 + 4

x + 9
```

The output of first line of code is not printed out because it is assigned to a variable instead.

The second line of output is printed out instead, but this means that the calculated value has not been saved for future use.

## Displaying Graphs

```{r}
plot(x = iris$Sepal.Length, y = iris$Sepal.Width)
```


